### 2020-01-31 paper/sex_selection_spacing-ver3.tex
Wrong graph titles
Shorten conceptual framework section

@@

To understand the potential implications of the substantial changes in income, female 
education, and female labor force participation that India has experience on birth
spacing, this section discuss relevant theoretical frameworks and prior findings 
on birth spacing.

@@

If the mother is unlikely to work in market work, as has become more common over time in 
India, there is little incentive to children more closely together for economic reasons.

% [TK not clear that these two paragraphs add anything to this section]
% The question is then why women appear to be leaving the labor force.
% With the strong economic growth in India, real wages for both men and women have almost 
% doubled between 1987 and 2011 \citep{Klasen2015}.
% Despite the increases in wages and the higher female education, the mean male wage is
% still close to 70 percent higher than the mean female wage and women’s labor supply 
% appear to be more negatively elastic to their husbands' wages than it is positively 
% elastic to own wages, suggesting that the reduction in female labor supply is driven by 
% an income effect \citep{Bhargava2018}.%
% \footnote{
% Furthermore, the development in women's wages is not uniform across education 
% levels \citep{Klasen2015,Bhargava2018}.
% The real wages for women with middle school education or below have converged. 
% For women with secondary education, the change over time depends on the sample used,
% with some showing a substantial decline and others a modest increase.
% Women with more than secondary education experienced an increased in their real 
% wages, especially in cities.
% }

% However, even after controlling for household characteristics and husband income, there 
% still is the U-shaped relationship between female education and labor supply shown
% above with the lowest labor force participation for women with secondary 
% education \citep{Chatterjee2018}.
% There are two possible explanations for this effect, both directly related to the strong
% pro-male bias in India.
% First, it becomes less socially acceptable for women to work in manual labor as their
% education increases, and women are still mostly excluded from white-collar
% employment despite robust economic growth \citep{Klasen2015,Chatterjee2018}.
% Second, with increasing education, women's productivity at home also increases, 
% especially in the production of offspring human capital.
% With relatively more boys born because of increased access to sex-selective 
% abortions and an increasing male income, demand for better-educated women can 
% increase, even if they do not participate in the labor market \citep{Behrman1999}.

With increasing income, parents may also prefer higher child ``quality'' and that would
also predict longer birth intervals since parental attention per child increases
\citep{Zajonc1975,Zajonc1976,Razin1980}.
The evidence on spacing's effect on child quality measures such as IQ 
and education is, however, mixed for developed countries and non-existing 
for developing countries
\citep{Powell1993,Pettersson-Lidbom2009,Buckles2012,Barclay2017}.
Nevertheless, for one crucial aspect of child quality---health and mortality---longer 
spacing does lead to better outcomes, although this relationship weakens with maternal 
education \citep{Whitworth2002,Conde-Agudelo2012,Molitoris2019}.

While one might expect that increasing income and female education would also lengthen
average birth spacing through access and knowledge of contraception, the empirical 
relationship between contraception use and birth spacing is ambiguous 
\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Yeakey2009,Kim2010,Soest2018}.
To further complicate the relationship between contraception and spacing, the ability 
to successfully use ``low efficacy'' contraceptive methods, such as the rhythm method, 
is increasing in education, while there is no difference across education levels 
when it comes to modern contraceptives such as pills or injectables 
\citep{Rosenzweig1989}.
Additionally, even in the absence of modern contraceptives, families appear able to 
time or at least postpone births when they have substantial enough incentive 
\citep{Jayachandran2011,Alam2018}.

The discussion has so far assumed that children are identical---except 
for any differences that arise from spacing---but there is substantial evidence 
that the sex composition of previous children affects birth spacing, with the
absence of boys significantly decreasing the duration to next birth
\citep{Haughton1995,Haughton1996,Rahman1993,Bhalotra2008,Kumar2016,Soest2018}.

If short spacing lowers the survival probability of the next child, it is not, however, 
apparent that we should expect shorter spacing in the absence of boys.
There are two potential reasons why parents might still try to conceive sooner 
in the absence of boys.
One possibility is that parents do not realize that short spacing is potentially
detrimental to the next child's health, resulting in high mortality for both boys 
and girls born after short spacing across all households.

With the adverse effects of shorter spacing strongly mitigated by higher education,
better-educated women can, in theory, have shorter spacing in the absence of a boy 
without substantial increasing mortality risk.
Differences in mortality outcomes across boys and girls are still possible,
but should not be as large as for less-educated women.

With the introduction of sex selection, parents can avoid the birth of girls, 
although at the cost of the procedure and having to wait longer until 
the next child if they abort the fetus.

Theory suggests that sex selection increases with lower desired fertility, and, for a 
given desired number of children, the higher the parity \citep{Portner2015b}.
The increased use of sex selection in India with education and in urban
areas is consistent with a lower desired fertility for both groups,
either because of the higher cost of children or because of other
changes in the preferred number of children
\citep{das_gupta97,retherford03b,jha06,Guilmoto2009a,Bongaarts2013,Portner2015b,
Jayachandran2017}.%
\footnote{
Stronger son preference could also contribute, but better-educated women 
have declining stated son preference over time \citep{bhat03,pande07}.
}

The higher the cost of prenatal sex determination and abortion, the less use we should 
see.
Similarly, any potential adverse effects on the mother and offspring 
from repeated abortions should also reduce the use of sex selection---provided that 
parents are aware of these costs.
Furthermore, the more abortions between births, the less the parents can take advantage 
of economies of scale.
Better-educated women tend to live in households with higher income, which better enables 
them to access prenatal sex determination and lowers the relative costs of using sex 
selection.

Given the increase in birth spacing with each abortion, parents may try to 
conceive even sooner to compensate for the potentially longer spacing and, 
thereby, still take advantage of economies of scale in childrearing.
Furthermore, if health outcomes for short spacing births have improved over 
time---as is likely---we should see an even stronger push toward shorter 
spacing for women using sex selection.

The increases in female educational attainment imply that access to education 
has expanded beyond the higher castes. 
However, ``Sanskritization'' implies that as lower castes females gain access to 
education and their husbands' income increases, the women adopt higher caste 
norms such as stronger son preference and a retraction from the formal labor 
market \citep{Srinivas1956,Chen1995,Abraham2013,Chatterjee2018}. 
``Sanskritization'' may also lead to an increased aversion to daughters, rather 
than just an increased preference for sons, which, in turn, lowers desired 
fertility \citep{Borooah2004}.

Hence, with substantial increases in husband income and a declining female labor force 
participation, I expect a push toward longer birth spacing over time, independent
of education levels, based on the income effects and the effects of spacing
on child outcomes in the theories above.
The declining percentage of women working suggests that the opportunity cost
effects with increasing education will not be strong enough to shorten the
birth spacing.

As desired fertility decreases with increasing education, I, furthermore, expect 
birth spacing to increase the most among the best-educated because of their 
use of sex selection and because of "Sanskritization" the changing composition 
of women in the better-educated group does not substantially change this 
group's use of sex selection.
Working in the opposite direction is that women with more education can space
their children closer together without substantially increasing child mortality risk.

@@

\section{How Much has Fertility Really Fallen?\label{sec:fertility}}

@@

@@

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{1972-1984}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p1_med_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p1_med_dummies} 
    \end{minipage}
}
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p1_med_dummies}
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{1985-1994}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p2_med_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p2_med_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p2_med_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{1995-2004}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p3_med_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p3_med_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p3_med_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{2005-2016}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p4_med_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p4_med_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p4_med_dummies} 
    \end{minipage}
} 
\caption{Predicted Probability of Infant Mortality for women with no education}
\label{fig:mortality_med}
\end{figure}

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{1972-1984}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p1_high_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p1_high_dummies} 
    \end{minipage}
}
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p1_high_dummies}
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{1985-1994}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p2_high_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p2_high_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p2_high_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{1995-2004}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p3_high_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p3_high_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p3_high_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{2005-2016}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p4_high_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p4_high_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p4_high_dummies} 
    \end{minipage}
} 
\caption{Predicted Probability of Infant Mortality for women with no education}
\label{fig:mortality_high}
\end{figure}

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{1985-1994}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p2_highest_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p2_highest_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p2_highest_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{1995-2004}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p3_highest_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p3_highest_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p3_highest_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{2005-2016}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p4_highest_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p4_highest_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p4_highest_dummies} 
    \end{minipage}
} 
\caption{Predicted Probability of Infant Mortality for women with no education}
\label{fig:mortality_highest}
\end{figure}

>>>>

A question is whether the rapid expansion in female educational attainment has led
to significant changes in the composition of better-educate women and whether this will
affect their son preference and desired fertility.
It is clear that the increases in female educational attainment imply that access to 
education has expanded beyond the higher castes. 
However, ``Sanskritization'' implies that as lower castes females gain access to 
education and their husbands' income increases, the women adopt higher caste 
norms such as stronger son preference and a retraction from the formal labor 
market \citep{Srinivas1956,Chen1995,Abraham2013,Chatterjee2018}.

@@

To understand the potential implications for birth spacing of the substantial changes in 
income, female education, and female labor force participation that India has experienced, 
this section discuss relevant theories and prior findings on birth spacing.

@@

The low and declining female labor force participation, especially for younger women, 
suggests, however, that families face little incentive to space children more closely 
together for economic reasons.
This may happen if household income has increased so substantially that the income effect 
dominates any substitution effect.
Two findings speak for this effect.
First, although real wages for both men and women have almost doubled between 1987 and 
2011, the mean male wage is still close to 70 higher than the female wage 
\citep{Klasen2015,Bhargava2018}.
Second, women’s labor supply appear to be more negatively elastic to their husbands' 
wages than it is positively elastic to own wages \citep{Bhargava2018}.

In fact, it may be that the combination of rising incomes and continued son preference 
lead to even longer spacing than what we would expect from the standard income effect.
As women's education increases, their productivity at home also increases, especially in 
the production of offspring human capital.
With relatively more boys born because of increased access to sex-selective 
abortions and an increasing potential income for (male) offspring, demand for 
better-educated women can increase, even if they do not participate in the labor market 
\citep{Behrman1999}.
The result would be longer birth intervals because that increases parental attention 
per child resulting in higher child ``quality'' \citep{Zajonc1975,Zajonc1976,Razin1980}.
The evidence on spacing's effect on child quality measures such as IQ 
and education is, however, mixed for developed countries and non-existing 
for developing countries
\citep{Powell1993,Pettersson-Lidbom2009,Buckles2012,Barclay2017}.
Nevertheless, for one crucial aspect of child quality---health and mortality---longer 
spacing does lead to better outcomes, although this relationship weakens with maternal 
education \citep{Whitworth2002,Conde-Agudelo2012,Molitoris2019}.

While one might expect that increasing income and female education would also lengthen
average birth spacing through better access and knowledge of contraception, the empirical 
relationship between contraception use and birth spacing is ambiguous 
\citep{Tulasidhar1993,Whitworth2002,Bhalotra2008,Yeakey2009,Kim2010,Soest2018}.
Furthermore, the ability to successfully use ``low efficacy'' contraceptive methods, 
such as the rhythm method, is increasing in education, while there is no difference 
across education levels when it comes to modern contraceptives such as pills or 
injectables \citep{Rosenzweig1989}.

With the introduction of sex selection, parents can avoid the birth of girls, 
although at the cost of the procedure and having to wait longer until the next child 
if each aborted pregnancy.
Theory suggests that sex selection increases with lower desired fertility, and, for a 
given desired number of children, the higher the parity \citep{Portner2015b}.
The increased use of sex selection in India with education and in urban
areas is consistent with a lower desired fertility for both groups
\citep{das_gupta97,retherford03b,Guilmoto2009a,Portner2015b,Jayachandran2017}.
Better-educated women also tend to live in households with higher income, which better 
enables them to access prenatal sex determination and lowers the relative costs of using 
sex selection and have long birth intervals.

In summary, with substantial increases in husband income and a declining female labor 
force participation, I expect a push toward longer birth spacing over time, independent
of education levels, based on the income effects and the effects of spacing
on child outcomes.
As desired fertility decreases with increasing education, I, furthermore, expect 
birth spacing to increase the most among the best-educated because of their 
use of sex selection and because of with "Sanskritization" the changing composition 
of women in the better-educated group does not substantially change this 
group's use of sex selection.%
\footnote{
Working in the opposite direction is that women with more education can space
their children closer together without substantially increasing child mortality risk,
although compared with those factors this effect is likely to be relatively small.
}

@@

\section{What has Happened to Fertility?\label{sec:fertility}}

@@

[From conceptual framework section]
If short spacing lowers the survival probability of the next child, it is not, however, 
apparent that we should expect shorter spacing in the absence of boys.
There are two potential reasons why parents might still try to conceive sooner 
in the absence of boys.
One possibility is that parents do not realize that short spacing is potentially
detrimental to the next child's health, resulting in high mortality for both boys 
and girls born after short spacing across all households.

With the adverse effects of shorter spacing strongly mitigated by higher education,
better-educated women can, in theory, have shorter spacing in the absence of a boy 
without substantial increasing mortality risk.
Differences in mortality outcomes across boys and girls are still possible,
but should not be as large as for less-educated women.
[end fro conceptual framework section]

@@

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{1972-1984}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p1_med_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p1_med_dummies} 
    \end{minipage}
}
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p1_med_dummies}
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{1985-1994}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p2_med_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p2_med_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p2_med_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{1995-2004}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p3_med_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p3_med_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p3_med_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{2005-2016}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p4_med_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p4_med_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p4_med_dummies} 
    \end{minipage}
} 
\caption{Predicted Probability of Infant Mortality for women with one to
seven years of education}
\label{fig:mortality_med}
\end{figure}

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{1972-1984}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p1_high_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p1_high_dummies} 
    \end{minipage}
}
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p1_high_dummies}
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{1985-1994}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p2_high_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p2_high_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p2_high_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{1995-2004}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p3_high_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p3_high_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p3_high_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{2005-2016}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p4_high_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p4_high_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p4_high_dummies} 
    \end{minipage}
} 
\caption{Predicted Probability of Infant Mortality for women with eight
to eleven years of education}
\label{fig:mortality_high}
\end{figure}

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{1985-1994}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p2_highest_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p2_highest_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p2_highest_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{1995-2004}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p3_highest_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p3_highest_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p3_highest_dummies} 
    \end{minipage}
} 
\\
\rotatebox[origin=c]{90}{\small{2005-2016}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s2_p4_highest_dummies}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s3_p4_highest_dummies} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{mortality_s4_p4_highest_dummies} 
    \end{minipage}
} 
\caption{Predicted Probability of Infant Mortality for women with twelve or
more years of education}
\label{fig:mortality_highest}
\end{figure}
